Article 2:	Information-Seeking Behaviors for Information on Covid-19 Vaccinations

### 2022-01-26 paper2.Rmd
conclusion written

---
title: "Article 2:	Information-Seeking Behaviors for Information on Covid-19 Vaccinations"
author: "Kelsey Gonzalez"
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options:
  chunk_output_type: console
output:
  bookdown::word_document2: 
    toc: true
    reference_docx: StylesTemplate.docx
  bookdown::pdf_document2:
    latex_engine: xelatex
    number_sections: true
header-includes:
   - \usepackage{siunitx}
   - \usepackage{setspace}
   - \usepackage{dcolumn}
   - \usepackage{caption}
   - \usepackage{longtable}
   - \usepackage{booktabs}
   - \doublespacing
   - \usepackage{placeins}
csl: american-sociological-association.csl
bibliography: "My Library.bib"
indent: true
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      cache = TRUE,
                      fig.width = 7,
                      fig.asp = 0.8,
                      out.width = "80%",
                      fig.align="center"
                      # dev.args = list(png = list(type = "cairo"))
                      )

@@

conf_int_prop <- function(var){
  p <- mean(!!var, na.rm = T)
  q <- 1 - p
  n <- nrow(rain)
  min <- p - 1.96*sqrt((p*q)/n)
  max <- p + 1.96*sqrt((p*q)/n) 
  paste0(round(min, 2), ", ", round(max, 2))
}
print_perc <- function(var){
  label_percent()(mean(var, na.rm = T))
}

@@

@@

Information is especially important given the prominent trends of
misinformation, disinformation, and mistrust in traditional institutions
[@starbird19; @kata10]. While no belief in false information can be thought of as
harmless [@douglas21] some discredited theories such as 'vaccines cause autism'
have major ramifications for both the individual and the social world that
surrounds them. For example, a newfound public resistance to vaccination
against Measles by so-called 'anti-vaxxers' caused a 17% increase in rates
worldwide in 2019. This increase killed  142,000 people, most of whom were
children under the age of five [@givetash19]. However, even in the ever-evolving
research agenda of misinformation and infodemiology [@eysenbach02], much of the
research focuses on the supply side of information, like spaces where
individuals first encounter with conspiracy theories or other information
[@johnsonOnlineCompetitionPro2020; @broniatowski_etal20].
<!-- cite something else here -->

The lack of research in this area makes it quite unclear how individuals choose
to search for information through the multimedia environment of the 21st
century. Even outside of the misinformation literature, much of the research
conducted in social networks and communication focus on senders, influencers,
and persuasion strategies [@mertonManifestLatentFunctions1968;
@katzPersonalInfluencePart1955; @lazarsfeldPeopleChoice1944 ], rather than on
“the receiver as an active information seeker and processor."   [@johnsonComprehensiveModelCancerRelated1993; though there are always exceptions 
@eysenbach09].

<!-- TODO cleanup -->
For this paper, I will use the case of Covid-19 vaccinations to explore the
variation among information search vehicles. T

Research Questions

* How do computer-mediated or interpersonal network information-seeking strategies vary across populations? 
* What factors lead people to perform health information search online versus among social network ties? 
* How does the utilization of social networks, search engines, and social media as vary in the case of searching for information on the Covid-19 vaccine?

<!-- TODO  cleanup -->

@@

Active directed searching by individuals to obtain information is sparsely
discussed in the sociological literature. Pejtersen
[-@pejtersenDesignComputeraidedUsersystem1984], a scholar of library and
information science, theorized that there are 5 strategies for searching for
information. The most common strategy is browsing, where people follow leads
based on associations without premeditation. Another strategy is analytical,
which includes an explicit consideration of all facets of the question to guide
a search. The empirical method guides the search based on tactics that were
successful in past research. The known site strategy is to go to the direct
source of the information if known. And finally, the similarity method is to
find information based on another similar question that already has an answer.
These 5 strategies vary in their demands for prior knowledge, cognitive
processing, memory, and time spent. While this theory is aimed at finding
information in a library setting, scholars have extended the theory to other
fields and validated the framework [@fidelHumanInformationInteraction2012]; the
frame is a useful beginning point for my theories of information search through
network activation or through computer-mediated communication.

Some communication theorists ask why an answer to a question is sought in the
first place. The Theory of Uncertainty Management
[@brashersCommunicationUncertaintyManagement2001] professes that people search
for information when their uncertainty around the subject leads to anxiety or
other cognitive harms. The Theory of Motivated Information Management
[@afifiTheoryMotivatedInformation2004; @afifiSeekingInformationSexual2006]
extends the prior by adding that uncertainty itself is not the catalyst for
information-search; rather, it is driven by a discrepancy between the current
level of uncertainty on a subject and desired level of uncertainty.

One way to find information is to activate network ties to find out information
through a form of social support. Social support, while previously used
interchangeably with the term social networks and social integration
[@houseStructuresProcessesSocial1988], are the emotional, informational, and
instrumental assistance functions performed between social ties and have strong
and measurable association with health outcomes
[@houseMeasuresConceptsSocial1985; @thoitsMechanismsLinkingSocial2011].
Informational support is the process of seeking “help in defining,
understanding, and coping with problematic events and include education, advice,
or referral to another source of support” [@winemiller_etal93, p. 640].
Brashers, a health communications researcher, defines informational support
slightly differently, focusing on the exchange of information that “facilitates
coping with life stresses… that may be exchanged among members of a support
network” [-@brashersInformationSeekingAvoiding2002, p. 260]. <!--  Both of these
definitions provide important lenses for my question of how computer-mediated or
interpersonal information-seeking strategies vary.--> If information is needed
but there is no search for coping or deeper understanding of important matters,
people are likely to choose to search online.

Core discussion networks are the default lens to investigate network resources
and social support in surveys. The underlying assumption is that individuals
reach out to a handful of strong ties when in need of support, which can be
elicited in surveys using name generators [@marsdenCoreDiscussionNetworks1987].
This approach has yielded important insights, but largely overlooks crucial
processes of resource activation [@hurlbertCoreNetworksTie2000;
@perrySocialNetworkActivation2015; @smithDonPutMy2005]. Small
[-@smallSomeoneTalk2017] shows that the core discussion network does not capture
how people activate social support in practice and indicates that people draw on
much broader social connections for support, also calling back to the weak ties
research by Granovetter [-@granovetterStrengthWeakTies1973]. There is ongoing
research investigating how weak-tie support holds for different support types
based on the architecture put forward by House, Umberson, and Landis
[-@houseStructuresProcessesSocial1988] of instrumental, emotional, and
informational support. I follow the definition of Cohen and Wills
[-@cohenStressSocialSupport1985] and define informational support as “help in
defining, understanding,  and coping with problematic events and include
education, advice, or referral to another source of  support”
[@winemiller_etal93, p. 640].

However, informational support can also be sought outside of the social network
context, namely via computer-mediated information search tools such as the
process of “Googling”. As the online environment began penetrating all facets of
modern human life, it makes sense that performing online search has become one
of the most convenient vehicles for information search. While Small
[-@smallSomeoneTalk2017] focuses on how support can depend on a network tie
simply "happened to be there", online search is theoretically the most
frictionless and costless mode of support. There are three computer-mediated
vehicles I consider for this analysis: search engines like Google, posting
questions on online forums like subreddits or Facebook groups, and posting a
status update online via Facebook or Twitter. The first two comprise what I call
“online search”, while the third is conceptually distinct and important to
include in the survey; yet it is a hybrid of social network activation and
online search.

From studies of mass communication, uses and gratifications theory (UGT)
[@blumlerUsesMassCommunications1974; @tanMassCommunicationTheories1985] may also
lend itself to theorizing why computer-mediated or interpersonal
information-seeking strategies vary. UGT posits that users are not passive
consumers of media and that people have an active role in choosing different
sources of media based on their satisfaction of specific needs on an individual
basis. UGT is based on Maslow’s [-@maslowTheoryHumanMotivation1943] hierarchy of
needs and is compatible with Lazarsfeld and Katz’s theory of two-step flow
[-@katzPersonalInfluencePart1955] because people can choose their media and the
opinion leaders they follow. Modern-day theorists have extended UGT theory and
classified the uses and gratifications of the internet and of social media.
Stafford, Stafford, and Schkade [-@staffordDeterminingUsesGratifications2004]
theorize that the internet provides gratification through useful content that
meets expectations, gratification from purposeful navigating or random browsing
as a process, and social gratification from forming and deepening social ties.
Leung [-@leungGenerationalDifferencesContent2013] theorizes that social media is
gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection, and
fulfills cognitive needs. Adapting UGT to my own purposes, I theorize that
informational support will be activated from network ties when the informational
need is related to forming and deepening social ties but search will be
conducted online when information is needed but an individual does not have an
additional cognitive need to fill through social interaction. Alternative goals
such as identity management or relational maintenance
[@brashersInformationSeekingAvoiding2002] need to be balanced and will determine
where search is conducted.

<!-- connect above and below paragraph to flow together -->
<!-- TODO  cleanup -->

As online search or interaction also allows increased anonymity, no or lowered
social cost, and the potential avoidance of embarrassment and other negative
social interactions, I theorize that most people who searched for
information will have done so online.

there are theoretical reasons why individuals would choose to search for
information among their network ties instead of online search. For instance,
Rains [-@rainsCopingIllnessDigitally2018] finds that patients tend to search for
technical information about an illness online but turn to their social network
for experiential information from others facing similar circumstances in the
case of cancer. Moreover, if an individual distrusts the medical establishment,
or popular media, they may be more likely to activate informational support
among their social network or turn to online groups that validate their
worldview [@bogersHowSocialAre2014].

<!-- TODO add a hypothesis here -->

@@

datasummary(formula = 
  (`Received info` = receive_i) +
    (`Received info, Doctor` = receive_i_fr_dr) +
    (`Received info, Person` = receive_i_fr_pers) +
    (`Received info, News` = receive_i_fr_tv) +
    (`Received info, Social Networking Site` = receive_i_fr_onlnet) +
    (`Received info, Online Forum` = receive_i_fr_onlgroup) +
    (`Sought Info` = int_sought) +
    (`Sought Info, Doctor` = int_sought_fr_dr) +
    (`Sought Info, Person` = int_sought_fr_pers) +
    (`Sought Info, Social Networking Site` = int_sought_fr_onlnet) +
    (`Sought Info, Online Forum` = int_sought_fr_onlgroup) +
    (`Sought Info, Online Search` = int_sought_fr_onlsearch) +
    (`Vaccination Status` = vacc_status) +
    (`Vaccination Favorability` = vacc_view_pos) +
    (`Age` = age) +
    (`Hispanic or Latino/x` = hispanic) +
    (`Race, White` = race_white) +
    (`Race, Black` = race_black) +
    (`Race, Native American` = race_nat) +
    (`Race, Asian or Pacific Islander` = race_asian) +
    (`Associate's Deg or above` = college)  ~ 
    (Mean + SD) ,
  data = desc_table,
  fmt = '%.2f',
  title = 'Descriptive Statistics for Dichotomous and Numeric Variables',
  notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")),
  output = "kableExtra") %>% 
  kable_styling(latex_options = c("hold_position", "striped"))

@@

```{r}
vacc_status_freq <- rain[!is.na(rain$vacc_status_future),] %>% 
  group_by(col = vacc_status_future) %>% 
  summarise(n = n()) %>%
  mutate(n = n / sum(n))
```
Another Dependent variable for this analysis is a dichotomous variable
indicating whether the respondent has received a vaccination against Covid-19 or
plans to. For this survey, the number of doses or timeline of receipt were less
relevant to the research question. This variable instead focuses on intent or
opinion about the vaccine. About `r print_perc(rain$vacc_view_pos)` have a
positive view about the vaccine. This construct is made through the combination
of  two survey items. The first item is actual vaccination status, obtained through 
the question 'Did you receive a Covid-19 vaccine?'.
`r print_perc(rain$vacc_status)` of the sample said that
they had indeed received a vaccination (95% Confidence Interval = \{`r conf_int_prop(rain$vacc_status)`\}). As the national vaccination rate is
closer to 55% (CITE), this indicates some bias in our sample that must be
acknowledged: either MTurkers are more likely to be vaccinated that the normal
population (sampling bias) or there is some conformity bias in the responses
causing survey takers to provide false answers. The second survey item that
contributes to 'Vaccination Outlook' was only given to those who had not
responded 'yes' to the to their vaccination status. These respondents were asked 'Do you
plan to receive a vaccine for the prevention of the Covid-19 virus?'. Of those
who were asked this question (n = `r nrow(rain[!is.na(rain$vacc_status_future),])`),
`r label_percent()(filter(vacc_status_freq, col == 'Definitely yes') %>% pull(n))`
said they were 'definitely yes' getting the vaccine; 
`r label_percent()(filter(vacc_status_freq, col == 'Probably yes') %>% pull(n))` 
said they were 'probably yes' going to receive vaccine. The rest of the sample was more unsure: 
`r label_percent()(filter(vacc_status_freq, col == 'Might or might not') %>% pull(n))`
said they 'Might or might not', 
`r label_percent()(filter(vacc_status_freq, col == 'Probably not') %>% pull(n))`
said 'Probably not', and finally
`r label_percent()(filter(vacc_status_freq, col == 'Definitely not') %>% pull(n))`
said they would 'definitely not' receive the vaccine. The variable 'Vaccination
Outlook' indicates that either the respondent received a Covid-19 vaccine or
either probably or definitely will in the future.

### Independent Variables
The first independent variables used in this analysis are based on the question, 
'In the past 12 months, without searching for it, did you receive information
about the Covid-19 vaccine from … (check all sources you received information
from)'. This differs from the 'How did you look for information' question above
because it is based on passive reception of information. The largest proportion
of respondents had received information from a person like friend, neighbor, or
family member that [they] know ($\widehat{p}$ = `r print_perc(rain$receive_i_fr_pers)`
). Respondents also commonly received information from a television news channel
or a newspaper, about `r print_perc(rain$receive_i_fr_tv)` of the sample.
`r print_perc(rain$receive_i_fr_dr)` of the sample had received information from
their doctor or other health professional while `r print_perc(rain$receive_i_fr_onlnet)` 
received information from a social networking site such as Facebook timeline,
Twitter status update, or LinkedIn. Finally, the lowest proportion of the sample
had received information from an online discussion group, listserve, or other
online forum like a Facebook group or subreddit 
($\widehat{p}$ = `r print_perc(rain$receive_i_fr_onlgroup)`).

@@

# Results
```{r clean_before_reg}
rain <- rain %>% 
  mutate(across(c(receive_i,
                  receive_i_fr_dr,
                  receive_i_fr_pers,
                  receive_i_fr_tv,
                  receive_i_fr_onlnet,
                  receive_i_fr_onlgroup,
                  int_sought,
                  int_sought_fr_pers,
                  int_sought_fr_dr,
                  int_sought_fr_onlgroup,
                  int_sought_fr_onlnet,
                  int_sought_fr_onlsearch,
                  int_sought_affect,
                  vacc_status,
                  vacc_view_pos,
                  hispanic,
                  race_white,
                  race_black,
                  race_nat,
                  race_asian, 
                  college), ~ factor(.x, levels = c(0, 1))))

@@

mod1 <- glm(formula = int_sought ~ 
              receive_i_fr_dr +   
              receive_i_fr_pers +   
              receive_i_fr_tv +   
              receive_i_fr_onlnet +   
              receive_i_fr_onlgroup +   
              age + 
              gender + 
              race_white +   
              race_black +    
              race_nat +      
              race_asian +  
              hispanic  + 
              college,
            data = rain, family = binomial(link="logit"))
nullmod1 <- glm(formula = int_sought ~ 1,
            data = rain, family = binomial(link="logit"))
psuedor2 <- as.numeric(1-(logLik(mod1)/logLik(nullmod1)))

@@

To further investigate how people search for information, I asked those who had
sought information out intentionally, "How did you look for information about
the Covid-19 vaccine?" Because respondents could select as many responses as
applicable, each response is recorded as a dichotomous variable. I first
investigate how each Information Search Vehicle are related to each other using
the Phi Coefficient ($\\phi$) of binary association between each Information
Search Vehicle pair. The Phi coefficient can be interpreted like a correlation
coefficient, with numbers closer to -1 or positive one indicating a very strong
relationship [@warrens08]. Table \@ref(tab:model-2-phi) shows the results of
these coefficients. Out of the five information search vehicles investigated,
there is evidence that the vehicles are distinctly different concepts because
most coefficients fall under 0.3, the general rule of thumb for correlation 
coefficients to indicate a relationship. There does seem to be a relationship
between Online Forums and Social Networking Sites, possibly due to an
individual's propensity to use online networks over in-person networks. These
coefficients indicate a weak relationship between any two vehicles of
information search and that respondents in my sample utilize each of these a
little bit differently.

@@

part2_models[['Doctor']] <- glm(formula = int_sought_fr_dr ~ 
           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
           age + gender + college +
           race_white + race_black + race_nat + race_asian + hispanic,  
         data = rain, family = binomial(link="logit"))

part2_models[['Person']] <- glm(formula = int_sought_fr_pers ~ 
           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
           age + gender + college +
           race_white + race_black + race_nat + race_asian + hispanic,  
         data = rain, family = binomial(link="logit"))

>>>>

---
title: "Article 2:	Information-Seeking Behaviors for Information on Covid-19 Vaccinations"
author: "Kelsey Gonzalez"
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options:
  chunk_output_type: console
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    number_sections: true
  bookdown::word_document2: 
    toc: true
    reference_docx: StylesTemplate.docx
header-includes:
   - \usepackage{siunitx}
   - \usepackage{setspace}
   - \usepackage{dcolumn}
   - \usepackage{caption}
   - \usepackage{longtable}
   - \usepackage{booktabs}
   - \doublespacing
   - \usepackage{placeins}
csl: american-sociological-association.csl
bibliography: "My Library.bib"
indent: true
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      # cache = TRUE,
                      fig.width = 7,
                      fig.asp = 0.8,
                      out.width = "80%",
                      fig.align="center"
                      # dev.args = list(png = list(type = "cairo"))
                      )

@@

conf_int_prop <- function(var){
  p <- mean(!!var, na.rm = T)
  q <- 1 - p
  n <- nrow(rain)
  min <- p - 1.96*sqrt((p*q)/n)
  max <- p + 1.96*sqrt((p*q)/n) 
  paste0(label_percent()(min), ", ", label_percent()(max))
}
print_perc <- function(var){
  label_percent()(mean(var, na.rm = T))
}

@@

Keywords: Information-Seeking Behavior, Covid-19, Vaccine Hesitancy, Social Networks,

@@

Information is especially important given the prominent trends of
misinformation, disinformation, and mistrust in traditional institutions
[@starbird19; @kata10]. While no belief in false information can be thought of as
harmless [@douglas21] some discredited theories such as 'vaccines cause autism'
have major ramifications for both the individual and the social world that
surrounds them. For example, a newfound public resistance to vaccination
against Measles by so-called 'anti-vaxxers' caused a 17% increase in rates
worldwide in 2019. This increase killed  142,000 people, most of whom were
children under the age of five [@givetash19]. However, even in the ever-evolving
research agenda of misinformation and infodemiology [@eysenbach02], much of the
research focuses on the 'push' or 'supply' side of information, like spaces where
individuals first encounter with conspiracy theories or other information
[@johnsonOnlineCompetitionPro2020; @broniatowski_etal20].
<!-- cite something else here -->

The lack of research in which vehicles are likely to be chosen when an
individual faces a need for information makes it difficult for policy makers to
propose effective information campaigns that promote the health and wellbeing of
individuals in our society. Even outside of the misinformation literature, much
of the research conducted in social networks and communication focus on senders,
influencers, and persuasion strategies [@mertonManifestLatentFunctions1968;
@katzPersonalInfluencePart1955; @lazarsfeldPeopleChoice1944 ], rather than on
“the receiver as an active information seeker and processor."
[@johnsonComprehensiveModelCancerRelated1993; though there are always exceptions
@eysenbach09].

I use the case of information around Covid-19 vaccinations to explore the
variation of usage of information search vehicles. In doing so, I seek to answer
how computer-mediated or interpersonal information-seeking strategies vary
across populations in their search for information about Covid-19 vaccinations
and investigate how these strategies affect vaccination uptake.

Before addressing my central research questions, I offer an overview of the
current state of social science literature in regards to infromation-seeking
strategies before providing a description of the research methodology and
analytic sample. I discuss the implications of these findings for the
sociological understanding of information search and vaccination uptake.

@@

Active, directed searching by individuals to obtain information is sparsely
discussed in the sociological literature. Pejtersen
[-@pejtersenDesignComputeraidedUsersystem1984], a scholar of library and
information science, theorized that there are 5 strategies for searching for
information. The most common strategy is browsing, where people follow leads
based on associations without premeditation. Another strategy is analytical,
which includes an explicit consideration of all facets of the question to guide
a search. The empirical method guides the search based on tactics that were
successful in past research. The known site strategy is to go to the direct
source of the information if known. And finally, the similarity method is to
find information based on another similar question that already has an answer.
These 5 strategies vary in their demands for prior knowledge, cognitive
processing, memory, and time spent. While this theory is aimed at finding
information in a library setting, scholars have extended the theory to other
fields and validated the framework [@fidelHumanInformationInteraction2012]; the
frame is a useful beginning point for my theories of information search through
network activation or through computer-mediated communication.

Some communication theorists ask why an answer to a question is sought in the
first place. The Theory of Uncertainty Management
[@brashersCommunicationUncertaintyManagement2001] professes that people search
for information when their uncertainty around the subject leads to anxiety or
other cognitive harms. The Theory of Motivated Information Management
[@afifiTheoryMotivatedInformation2004; @afifiSeekingInformationSexual2006]
extends the prior by adding that uncertainty itself is not the catalyst for
information-search; rather, it is driven by a discrepancy between the current
level of uncertainty on a subject and desired level of uncertainty. In other
words, individuals only perform information search when they are distressed by
their lack of knowledge or understanding on a subject.

One way to find information is to activate network ties to find out information
through a form of social support. Social support, while previously used
interchangeably with the term social networks and social integration
[@houseStructuresProcessesSocial1988], are the emotional, informational, and
instrumental assistance functions performed between social ties and have strong
and measurable association with health outcomes
[@houseMeasuresConceptsSocial1985; @thoitsMechanismsLinkingSocial2011].
Informational support is the process of seeking “help in defining,
understanding, and coping with problematic events and include education, advice,
or referral to another source of support” [@winemiller_etal93, p. 640].
Brashers, a health communications researcher, defines informational support
slightly differently, focusing on the exchange of information that “facilitates
coping with life stresses… that may be exchanged among members of a support
network” [-@brashersInformationSeekingAvoiding2002, p. 260]. These definitions
help to differentiate between seeking information through social ties or through
something anonymous like online search; a need for coping or deeper
understanding of important matters is thought to sway that decision.

Social support has long been theorized to stem from core discussion networks and
much of the historical social support surveys only looked at these core
networks. The underlying assumption is that individuals reach out to a handful
of strong ties when in need of support, which could be elicited in surveys using
name generators [@marsdenCoreDiscussionNetworks1987]. This approach has yielded
important insights, but largely overlooks crucial
processes of resource activation [@hurlbertCoreNetworksTie2000;
@perrySocialNetworkActivation2015; @smithDonPutMy2005]. For instance, Small
[-@smallSomeoneTalk2017] shows that the core discussion network does not capture
how people activate social support in practice and indicates that people draw on
much broader social connections for support, reminiscent of the weak ties
research by Granovetter [-@granovetterStrengthWeakTies1973]. There is ongoing
research investigating how weak-tie support holds for different support types
based on the architecture put forward by House, Umberson, and Landis
[-@houseStructuresProcessesSocial1988] of instrumental, emotional, and
informational support.

However, informational support can also be sought outside of the social network
context, namely via computer-mediated information search tools such as the
process of “Googling”. As the online environment began penetrating all facets of
modern human life, it makes sense that performing online search has become one
of the most convenient vehicles for information search. While Small
[-@smallSomeoneTalk2017] focuses on how support can depend on a network tie
simply "happened to be there", online search is theoretically the most
frictionless and costless mode of support. No social capital or relationship is
necessary when chosing to utilize a search engine.

There are three computer-mediated vehicles I consider for this analysis: online
search engines like Google or Bing, posting questions on online forums like
subreddits or Facebook groups, and posting a status update online via Facebook
or Twitter. While the first two are largely anonymous and don't require a
personal network, the third is a unique hybrid between personal network
connections and online search.

There are important factors that can influence information-seeking strategies
besides the strength of social capital or ease of search. For instance, we can
borrow uses and gratifications theory (UGT) from studies of mass communication
[@blumlerUsesMassCommunications1974; @tanMassCommunicationTheories1985]. UGT
posits that users are not passive consumers of media and that people have an
active role in choosing different sources of media based on their satisfaction
of specific needs on an individual basis. UGT is based on Maslow’s
[-@maslowTheoryHumanMotivation1943] hierarchy of needs and is compatible with
Lazarsfeld and Katz’s theory of two-step flow [-@katzPersonalInfluencePart1955]
because people can choose their media and the opinion leaders they follow.
Modern-day theorists have extended UGT theory and classified the uses and
gratifications of the internet and of social media. Stafford, Stafford, and
Schkade [-@staffordDeterminingUsesGratifications2004] theorize that the internet
provides gratification through useful content that meets expectations,
gratification from purposeful navigating or random browsing as a process, and
social gratification from forming and deepening social ties. Leung
[-@leungGenerationalDifferencesContent2013] theorizes that social media is
gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection, and
fulfills cognitive needs.

Adapting these facets of UGT and social support to my own case, I theorize that
online search allows for increased anonymity, a lowered social cost, and the
potential avoidance of embarrassment and other negative social interactions,
especially in the case on search engines. Stephen Rains
[-@rainsCopingIllnessDigitally2018] finds that patients tend to search for
technical information about an illness online but they then turn to their social
network for experiential information from others facing similar circumstances in
the case of cancer. The type of information sought is therefore important.
If specific expertise on a specific topic is desired by a searcher, they may
reach out to personal connections that they see as expert such as a doctor, or
if an individual distrusts the medical establishment, they may be more likely to
activate informational support among their social network or turn to online
groups that validate their worldview [@bogersHowSocialAre2014]. Finally, UGT and
Brasher's definition of social support
[-@brashersInformationSeekingAvoiding2002] help us to theorize that the
psychosocial needs like identity management or relational maintenance
[@brashersInformationSeekingAvoiding2002] of an individual may influence their
chosen information search vehicle: when the informational need is related to
forming and deepening social ties search is likely to be done from network ties.

@@

datasummary(formula = 
  (`Received info` = receive_i) +
    (`Received info, Doctor` = receive_i_fr_dr) +
    (`Received info, Person` = receive_i_fr_pers) +
    (`Received info, News` = receive_i_fr_tv) +
    (`Received info, Social Networking Site` = receive_i_fr_onlnet) +
    (`Received info, Online Forum` = receive_i_fr_onlgroup) +
    (`Sought Info` = int_sought) +
    (`Sought Info, Doctor` = int_sought_fr_dr) +
    (`Sought Info, Person` = int_sought_fr_pers) +
    (`Sought Info, Social Networking Site` = int_sought_fr_onlnet) +
    (`Sought Info, Online Forum` = int_sought_fr_onlgroup) +
    (`Sought Info, Online Search` = int_sought_fr_onlsearch) +
    (`Vaccination Status` = vacc_status) +
    (`Vaccination Outlook` = vacc_view_pos) +
    (`Age` = age) +
    (`Hispanic or Latino/x` = hispanic) +
    (`Race, White` = race_white) +
    (`Race, Black` = race_black) +
    (`Race, Native American` = race_nat) +
    (`Race, Asian or Pacific Islander` = race_asian) +
    (`Associate's Deg or above` = college)  ~ 
    (Mean + SD) ,
  data = desc_table,
  fmt = '%.2f',
  title = 'Descriptive Statistics for Dichotomous and Numeric Variables',
  notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")),
  output = "kableExtra") %>% 
  kable_styling(latex_options = c("hold_position", "striped"))

@@

```{r}
vacc_status_freq <- rain[!is.na(rain$vacc_status_future),] %>% 
  group_by(col = vacc_status_future) %>% 
  summarise(n = n()) %>%
  mutate(n = n / sum(n))
```
Another Dependent variable for this analysis is a dichotomous variable
indicating whether the respondent has received or plans to receive a vaccination against Covid-19. For this survey, the number of doses or timeline of receipt were less
relevant to the research question. This variable instead focuses on intent or
opinion about the vaccine. About `r print_perc(rain$vacc_view_pos)` have a
positive view about the vaccine. This construct is made through the combination
of  two survey items. The first item is actual vaccination status, obtained through 
the question 'Did you receive a Covid-19 vaccine?'.
`r print_perc(rain$vacc_status)` of the sample said that
they had indeed received a vaccination (95% Confidence Interval = \{`r conf_int_prop(rain$vacc_status)`\}). As the national vaccination rate is
closer to 75% [@cdc20], this indicates some bias in our sample that must be
acknowledged: either MTurkers are more likely to be vaccinated that the normal
population (sampling bias) or there is some conformity bias in the responses
causing survey takers to provide false answers. The second survey item that
contributes to 'Vaccination Outlook' was only given to those who had not
responded 'yes' to the to their vaccination status. These respondents were asked 'Do you
plan to receive a vaccine for the prevention of the Covid-19 virus?'. Of those
who were asked this question (n = `r nrow(rain[!is.na(rain$vacc_status_future),])`),
`r label_percent()(filter(vacc_status_freq, col == 'Definitely yes') %>% pull(n))`
said they were 'definitely yes' getting the vaccine; 
`r label_percent()(filter(vacc_status_freq, col == 'Probably yes') %>% pull(n))` 
said they were 'probably yes' going to receive vaccine. The rest of the sample was more unsure: 
`r label_percent()(filter(vacc_status_freq, col == 'Might or might not') %>% pull(n))`
said they 'Might or might not', 
`r label_percent()(filter(vacc_status_freq, col == 'Probably not') %>% pull(n))`
said 'Probably not', and finally
`r label_percent()(filter(vacc_status_freq, col == 'Definitely not') %>% pull(n))`
said they would 'definitely not' receive the vaccine. The variable 'Vaccination
Outlook' indicates that either the respondent received a Covid-19 vaccine or
either probably or definitely will in the future.

### Independent Variables
The first independent variables used in this analysis are based on the question, 
'In the past 12 months, without searching for it, did you receive information
about the Covid-19 vaccine from … (check all sources you received information
from)'. This differs from the 'How did you look for information' question above
because this is based on passive reception of information. The largest proportion
of respondents had received information from a person like friend, neighbor, or
family member that [they] know ($\widehat{p}$ = `r print_perc(rain$receive_i_fr_pers)`
). Respondents also commonly received information from a television news channel
or a newspaper, about `r print_perc(rain$receive_i_fr_tv)` of the sample.
`r print_perc(rain$receive_i_fr_dr)` of the sample had received information from
their doctor or other health professional while `r print_perc(rain$receive_i_fr_onlnet)` 
received information from a social networking site such as Facebook timeline,
Twitter status update, or LinkedIn. Finally, the lowest proportion of the sample
had received information from an online discussion group, listserve, or other
online forum like a Facebook group or subreddit 
($\widehat{p}$ = `r print_perc(rain$receive_i_fr_onlgroup)`).

@@

# Results
```{r clean_before_reg}
rain_mod <- rain %>% 
  mutate(across(c(receive_i,
                  receive_i_fr_dr,
                  receive_i_fr_pers,
                  receive_i_fr_tv,
                  receive_i_fr_onlnet,
                  receive_i_fr_onlgroup,
                  int_sought,
                  int_sought_fr_pers,
                  int_sought_fr_dr,
                  int_sought_fr_onlgroup,
                  int_sought_fr_onlnet,
                  int_sought_fr_onlsearch,
                  int_sought_affect,
                  vacc_status,
                  vacc_view_pos,
                  hispanic,
                  race_white,
                  race_black,
                  race_nat,
                  race_asian, 
                  college), ~ factor(.x, levels = c(0, 1))))

@@

mod1 <- glm(formula = int_sought ~ 
              receive_i_fr_dr +   
              receive_i_fr_pers +   
              receive_i_fr_tv +   
              receive_i_fr_onlnet +   
              receive_i_fr_onlgroup +   
              age + 
              gender + 
              race_white +   
              race_black +    
              race_nat +      
              race_asian +  
              hispanic  + 
              college,
            data = rain_mod, family = binomial(link="logit"))
nullmod1 <- glm(formula = int_sought ~ 1,
            data = rain_mod, family = binomial(link="logit"))
psuedor2 <- as.numeric(1-(logLik(mod1)/logLik(nullmod1)))

@@

To further investigate how people search for information, I asked those who had
sought information out intentionally, "How did you look for information about
the Covid-19 vaccine?" Because respondents could select as many responses as
applicable, each response is recorded as a dichotomous variable. Table 
\@ref(tab:table-1-desc) reveals differences in the prevalence of usage of the 
various information seeking vehicles: Around 40% of the sample has inquired for 
information from a doctor, a person, or using online search tool (
`r percent_format()(mean(rain$int_sought_fr_dr, na.rm = T))`, 
`r percent_format()(mean(rain$int_sought_fr_pers, na.rm = T))`,
`r percent_format()(mean(rain$int_sought_fr_onlsearch, na.rm = T))`) while my 
respondents used vehicles like online forums (
`r percent_format()(mean(rain$int_sought_fr_onlgroup, na.rm = T))`) and social
networking sites (`r percent_format()(mean(rain$int_sought_fr_onlnet, na.rm = T))`)
to seek out information at significantly lower rates. To investigate how each
Information Search Vehicle are related to each other using the Phi Coefficient
($\\phi$) of binary association between each Information Search Vehicle pair.
The Phi coefficient can be interpreted like a correlation coefficient, with
numbers closer to -1 or positive one indicating a very strong relationship
[@warrens08]. Table \@ref(tab:model-2-phi) shows the results of these
coefficients. Out of the five information search vehicles investigated, there is
evidence that the vehicles are distinctly different concepts because most
coefficients fall under 0.3, the general rule of thumb for correlation
coefficients to indicate a relationship. There does seem to be a relationship
between Online Forums and Social Networking Sites, possibly due to an
individual's propensity to use online networks over in-person networks. These
coefficients indicate a weak relationship between any two vehicles of
information search and that respondents in my sample utilize each of these a
little bit differently.

@@

part2_models[['Doctor']] <- glm(formula = int_sought_fr_dr ~ 
           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
           age + gender + college +
           race_white + race_black + race_nat + race_asian + hispanic,  
         data = rain_mod, family = binomial(link="logit"))

part2_models[['Person']] <- glm(formula = int_sought_fr_pers ~ 
           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
           age + gender + college +
           race_white + race_black + race_nat + race_asian + hispanic,  
         data = rain_mod, family = binomial(link="logit"))
